---
header-includes:
    - \usepackage{fancyhdr}
    - \fancyfoot[CO,CE]{OSC-Group - http://www.osc-lab.de - JMU Wuerzburg - Pharmazie}
    - \fancyfoot[LE,RO]{\thepage}
    - \usepackage{fontspec}
    - \setmainfont{FreeSans}
    
title: "TDM Report - Vancomycin"
output: 
  pdf_document:
    latexengine: xelatex
df_print: paged
date: "`r format(Sys.time(), '%d.%B %Y')`"


---
\setmainfont{FreeSans}
\addtolength{\headheight}{1.0cm} 
\pagestyle{fancyplain} 
\rhead{\includegraphics[height=1.2cm]{./logo_rechts.png}} 
\lhead{\includegraphics[height=1.2cm]{./logo_links.png}}
\renewcommand{\headrulewidth}{0pt}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **1. Patient characteristics**

  
Patient ID: **`r input$pat_ID`** 
  
Body weight: **`r input$WT`** kg 

Creatinine Clearance: **`r input$CRCL`** mL/min

Receives Dialysis: **`r input$has_dialysis`**

  
    
``` {r ind_pars, echo=FALSE}


```


# **2. Pathogen Information**

Pathogen:  **`r names(GLOB_PATHOGENS[as.numeric(input$choose_pathogen)])`**

MIC: **`r input$MIC`** mg/L

``` {r scheme, echo=FALSE}

```

# **Clinical Recommendation**

**`r input$choose_recommendation` **
  
 
`r input$report_comment`

`r if(input$additional_tdm){
"Additional TDM samples should be obtained"
} ` 

`r if(input$add_dur_info){
"Infusion Duration should not fall below 30 min. CAVE: Red-Man-Syndrome!"
} ` 

``` {r recomm, echo=FALSE}



```

# **Used Dataset**

Measured Plasmaconcentrations (Last 10 concentrations)

``` {r tdm, echo=FALSE}

kable(app_data$user_data_set, format = "latex")  %>%
    kable_styling(position = "left")

```

# **Simulated Plasmaconcentration**

  

```{r simulation, echo=FALSE}


```

# **2. Dose Adaptation**


```{r mcmc_res, echo=FALSE}
    plot(app_data$adapted_pk_plot)
```


# **MCMC Diagnostic Plots**

```{r mcmc_diag, echo=FALSE}

gridExtra::grid.arrange(app_data$mcmc_result[[4]]$p_iter_ETA1, app_data$mcmc_result[[4]]$p_dens_ETA1,    
                              app_data$mcmc_result[[4]]$p_iter_ETA2, app_data$mcmc_result[[4]]$p_dens_ETA2, 
                              app_data$mcmc_result[[4]]$p_iter_ETA3, app_data$mcmc_result[[4]]$p_dens_ETA3, nrow=3, ncol=2, widths=c(3,1))  

chart.Correlation(app_data$mcmc_result[[4]]$chain_data, histogram=TRUE)

```